Applying Automated Verification to Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\

### 2019-04-23 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\textcolor{red}{What is the relation of this paper with software engineering?}

@@

The main contribution of this approach is to allow that a list of PV components (PV panels, charge controllers, inverters and batteries) can be inputted to the system, and the algorithm using automated verification, and written in language C, can find the best technical and financial result.%, using non-deterministic variables and exploring the design-space
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Automated Verification Using Model Checking}
\label{sec:AutomatedVerification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw. Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}. Here we evaluate four state-of-the-art model checkers to formally optimize the sizing of PV designs w.r.t. user requirements.

>>>>

\textcolor{red}{What is the relation of this paper with software engineering (SE)?}

@@

The main contribution of this approach is to allow that a list of PV components (PV panels, charge controllers, inverters and batteries) can be inputted to the system, and the algorithm using automated verification, and written in language C, can find the best technical and financial result.

\textcolor{red}{We need to make our contributions stronger. Why the SE community would be interested in this paper? What are the main open problems we need them to solve here? Remember that this is a paper for new ideas... we don't need to make questions but we don't need to answer all of them.}

%, using non-deterministic variables and exploring the design-space
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Automated Verification Using Model Checking}
\label{sec:AutomatedVerification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw. Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}. Here we evaluate four state-of-the-art model checkers to formally optimize the sizing of PV designs w.r.t. user requirements.
